---
title: "cleaning"
author: "JJayes"
date: "25/04/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(scales)
library(glue)
library(stringi)
```

## Purpose

Cleaning the data scraped so that each wine is it's own row.

### Reading in data

```{r}
df_1 <- read_rds("data/reviews/reviews_first_10002021-04-26~09-49-pm.rds")

df_2 <- read_rds("data/reviews/reviews_second_10002021-04-26~11-04-pm.rds")

df_3 <- read_rds("data/reviews/reviews_third_10002021-04-26~11-58-pm.rds")

df <- bind_rows(df_1, df_2, df_3)
```

### Cleaning

Unnest data

```{r}
df <- df %>% 
  unnest(c(text)) %>% 
  select(-text)

```

Remove lines with no text

```{r}
df <- df %>% 
  filter(nchar(value) > 0)
```

I want to join again the review URL from the list of links to the df. I made a mistake with the scraping code.

```{r}

links <- read_rds("data/links/list_of_links_2021-04-26~01-59-pm.rds")

links <- links %>% 
  mutate(key = str_remove(text, "https://winemag.co.za/wine/review/"),
         key = str_replace_all(key, "-", " "),
         key = word(key)) %>% 
  mutate(key = glue("{page}-{key}"))

df <- df %>% 
  mutate(key = stri_trans_general(str = title, 
                                   id = "Latin-ASCII"),
         key = str_replace_all(key, "'", ""),
         key = str_replace_all(key, "[:punct:]", " "),
         key = str_to_lower(word(key))) %>% 
  mutate(key = glue("{page}-{key}"))

df <- df %>% 
  left_join(links %>% select(text, key), by = "key")

df <- df %>% 
  rename(review_url = text) %>% 
  select(-key)

```


```{r}
df <- df %>% 
  mutate(id = str_c(link, title)) %>% 
  group_by(id) %>% 
  mutate(review = paste0(value, collapse = " ")) %>% 
  ungroup()

df <- df %>% 
  select(-c(link, page, value))

df <- df %>% 
  distinct()

df <- df %>% 
  mutate(date = lubridate::dmy(date)) %>% 
  arrange(date)

df <- df %>% 
  mutate(review_number = row_number())
```

How many wines in this review?

```{r}
df <- df %>% 
  mutate(n_wines = str_count(review, 
                                     "(?=\\s[7-9][0-9](?!\\%|D|d))(\\s[7-9][0-9])"))
```

What are the scores of these wines?

```{r}
df <- df %>% 
  mutate(wine_scores = str_extract_all(review, 
                                       # this says look ahead and see if you can see a rating: a number between 70 and 99 that is not followed by a percentage sign (like 70% syrah) and a piece of text. If you see this number, then extract it as the score.
                                     "(?=\\s[7-9][0-9](?!\\%|D|d))(\\s[7-9][0-9])"))
```

What are the words for each review?

```{r}
df <- df %>% 
  unnest(wine_scores) %>% 
  mutate(wine_review_locations = str_locate_all(review, glue("{wine_scores}"))) %>% 
  unnest(wine_review_locations) %>%
  mutate(wine_review_locations = wine_review_locations[,1],
         wine_review_locations = as.numeric(wine_review_locations)) %>% 
  distinct(id, wine_scores, wine_review_locations, .keep_all = T) %>%
  group_by(id) %>% 
  arrange(wine_review_locations) %>% 
  ungroup() %>% 
  arrange(review_number)

```

How can we get the text for each wine in the review only?

```{r}
df <- df %>% 
  group_by(review_number) %>% 
  mutate(wine_index = row_number()) %>% 
  mutate(review_start = case_when(
    
    wine_index == 1 ~ 0,
    TRUE ~ lag(wine_review_locations)
    
  )) %>% 
  ungroup() %>% 
  arrange(review_number) %>% 
  mutate(text = if_else(n_wines > 1, substr(review, review_start, wine_review_locations), review))

df %>% view()
```

A bit of tidying up

```{r}
df <- df %>% 
  mutate(text = str_remove(text, "^[:space:][7-9][0-9]/100"),
         text = str_remove(text, "^[:space:][7-9][0-9]"))
```

Scores as numbers - remove other cols

```{r}
df <- df %>% 
  select(-c(wine_review_locations, wine_index, review_start, review)) %>% 
  mutate(wine_scores = parse_number(wine_scores))
```

Get price

```{r}
df <- df %>% 
  # get price from review
  mutate(price = str_extract(text, "R[1-9][0-9]+"),
         price_R = parse_number(price))


df %>% 
  ggplot(aes(wine_scores, price_R, colour = date)) +
  geom_smooth(method = "lm") +
  geom_jitter(alpha = .5) +
  scale_y_log10()

df %>% 
  ggplot(aes(date, wine_scores)) +
  geom_smooth(method = "lm") +
  geom_point(alpha = .1)
```

### Things still to get

- Vintage.

NICE!

```{r}

df <- df %>% 
  mutate(vintage = case_when(
    n_wines == 1 ~ str_extract(title, "[1-2][0-9][0-9][0-9]"),
    n_wines > 1 ~ if_else(str_detect(title, "[1-2][0-9][0-9][0-9]"), 
                          str_extract(title, "[1-2][0-9][0-9][0-9]"),
                          str_extract(text, "[1-2][0-9][0-9][0-9]")
    ),
    TRUE ~ "Error")) %>% 
  mutate(vintage = parse_number(vintage))

df %>% 
  filter(nchar(text) > 50) %>% 
  arrange(nchar(text)) %>% view()

```

- Varietals.

### Cleaning before using the text recipe

Need to remove all of the numbers and punctuation from the text and titles.

```{r}
df %>% 
  count(wine_scores, sort = T)

write_rds(df, "data/clean-data/reviews_2.rds")

```

