---
title: "wine-score-model"
author: "JJayes"
date: "25/04/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

devtools::install_github("tidymodels/parsnip")
library(tidyverse)
library(tidymodels)
```

## Purpose

make a model to predict wine score based on price, review date and words

### Reading in data

```{r}

df <- read_rds("data/clean-data/reviews_2.rds")

```

### Check data

```{r}
df <- df %>% 
  select(-price, -n_wines, -review_url, -id, -n_wines) %>% 
  filter(!is.na(price_R))

df %>% skimr::skim()
```

Have to impute missing vintages

### Setting up splits

```{r}
set.seed(123)
tidy_split <- initial_split(df, strata = wine_scores)

tidy_train <- training(tidy_split)
tidy_test <- testing(tidy_split)

set.seed(123)
tidy_folds <- vfold_cv(tidy_train, strata = wine_scores)

```



# Things to change in scraper and cleaning.

- wine scores to score
- price and price_R. Don't need both.
- varietal
- vintage

### Make a recipe

Things to think about in the recipe.

Remove stopwords.

use the pos filter to get rid of some things. keep only verbs, nouns and adjectives? see [textrecipes](https://textrecipes.tidymodels.org/reference/step_pos_filter.html)

```{r}
library(textrecipes)

wine_rec <- recipe(wine_scores ~ ., data = df) %>% 
  update_role(c(review_number), new_role = "id") %>% 
  step_date(date, keep_original_cols = F) %>%
  step_tokenize(text) %>% 
  step_tokenize(title) %>% 
  step_tokenfilter(text, max_tokens = 1000) %>% 
  step_tokenfilter(title, max_tokens = 500) %>% 
  # step_tfidf(text) %>%
  # step_tfidf(title) %>% 
  step_impute_knn(vintage) %>% 
  step_dummy(all_nominal_predictors()) 
  # step_normalize(all_numeric_predictors())

wine_rec %>% prep() %>% juice()
```

### Make a model spec

```{r}

xgb_spec <- boost_tree(trees = tune(),
                       min_n = tune(),
                       learn_rate = tune()) %>% 
  set_mode("regression") %>% 
  set_engine("xgboost")

svm_spec <- svm_linear() %>% 
  set_mode("regression") %>% 
  set_engine("LiblineaR")

```

### Make a parameter grid

```{r}

xgb_grid <- grid_regular(parameters(xgb_spec), 
                         levels = 5)

svm_grid <- grid_regular(parameters(svm_spec),
                         levels = 5)

svm_wf <- workflow() %>% 
  add_recipe(wine_rec) %>% 
  add_model(svm_spec)

```

### Apply the parameter grid to the model

```{r}
xgb_tune <- tune_grid(
  xgb_spec,
  wine_rec,
  resamples = tidy_folds,
  grid = xgb_grid
)
```

### Fit resamples to the 

```{r}
svm_res <- fit_resamples(
  svm_wf,
  tidy_folds,
  control = control_resamples(save_pred = T)
  
)
```

### Select best params with tune pacakge using rmse

```{r}
xgb_param <- xgb_tune %>% 
  select_best("rmse")

```

### Apply paramters to the model

```{r}
xgb_model <- finalize_model(xgb_spec, xgb_param)

```

### Workflow combines everything together - preprocessing, modelling, 

```{r}
xgb_wf <- workflow() %>% 
  add_model(xgb_model) %>% 
  add_recipe(wine_rec)

```

### Apply it to test set and extract metrics

```{r}
xgb_res <- last_fit(xgb_wf, tidy_split)

xgb_res %>% 
  unnest(.predictions)

metrics(xgb_res %>% unnest(.predictions), truth = wine_scores, estimate = .pred)

write_rds(xgb_res, "data/models/xbg_1.rds")
```

### Same for SVM

```{r}
metrics(svm_res %>% 
  unnest(.predictions), truth = wine_scores, estimate = .pred)

collect_metrics(svm_res)
```



```{r}
# this is the one to save it as a model
svm_final <- fit(
  svm_wf,
  df
  
)

# this one has it as a workflow
svm_final <- last_fit(
  svm_wf,
  tidy_split
  
)

svm_final %>% collect_metrics()

# write_rds(svm_final, "model.rds")

```

### Pull workflow fit

```{r}
svm_fit <- pull_workflow_fit(svm_final$.workflow[[1]])


tidy(svm_fit) %>% 
  filter(term != "Bias") %>%
  group_by(sign = estimate > 0) %>% 
  slice_max(abs(estimate), n = 20) %>% 
  ungroup() %>% 
  mutate(type = case_when(
    
    str_detect(term, "title") ~ "title",
    str_detect(term, "text") ~ "text",
    TRUE ~ "other")) %>% 
  mutate(term = str_remove(term, "tfidf_title_"),
         term = str_remove(term, "tfidf_text_")) %>% 
  mutate(term = fct_reorder(term, estimate)) %>% 
  ggplot(aes(estimate, term, fill = type)) +
  geom_col()

```

